Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-18 article.Rmd
Load the cached data
Remove sample IPUMS data

```

@@

**unfortunatley the first ten isn't intuitive since it's just "!" rather than names - this is going to confuse readers, I think**
```{r ipums_usa, echo=TRUE, results='markup'}
genderdata::ipums_usa
```

>>>>

# Load the data frames with the predicted gender, if they exist. Otherwise run
# the analysis.
if(file.exists("data/diss-predicted.rda") &
     file.exists("data/ahr-predicted.rda")) {
  load("data/diss-predicted.rda")
  load("data/ahr-predicted.rda")
} else {
  source("R/load-data.R")
  source("predict-gender.R")
}
```

@@
